---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# actcrime

<!-- badges: start -->
<!-- badges: end -->

The goal of `actcrime` is to provide an R interface to access ACT crime data.

## Installation

You can install the development version of actcrime from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("TengMCing/actcrime")
```

## Example

```{r example}
library(actcrime)
# Load the package
```

The package includes a built-in dataset, `act_crime_stat_2024_09_30`, which contains cleaned and structured ACT crime statistics sourced from [dataACT](https://www.data.act.gov.au/Justice-Safety-and-Emergency/ACT-Crime-Statistics/2egm-dieb/about_data) as of **February 22, 2025**.

```{r}
act_crime_stat_2024_09_30 |> tibble::as_tibble()
```

Additionally, the package provides the function `get_act_crime_stat()`, which allows users to download the latest available crime statistics.

```{r}
get_act_crime_stat()
``` 


